---
title: "shinyApp"
author: "NJL"
date: "06/06/2021"
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(plotly)
```

## Introduction

This is the **User Document** for the WeatherHistory App in the Shiny server.
The URL for the app is https://jol2kor.shinyapps.io/WeatherHistory/

## Overview

The App displays the weather conditions that were prevailing in the 3 cities, Bangalore, Mumbai and Chennai during the month of May 2021.

The Max, Min and Average temperature, also included are average Humidity and average Wind Speed can be displayed in the graph using appropriate selections.

### Date Range Selection
The user can select the date range using the slider, the default is the complete month of May.


```{r echo = FALSE}
            sliderInput(inputId = "date", label = "Date Range",
                        min = 1, max = 31,
                        value = c(1, 31))
```


### Choice of weather parameter

The selection of the weather parameter for viewing as a plot for the selected day range is through a radio button input. At any time only one parameter can be visualised.

The y axis label is also updated accordingly.

The default setting is Average Temperature.

However, when hovering over the data points on the plot, all the parameters for that date and city is displayed in a box.


```{r echo = FALSE}
            radioButtons(inputId = "ylabel", label = "Choose Param",
                         choices = list("Max Temp" = 3, "Min Temp" = 5, "Avg Temp" = 4,
                                        "Avg Humidity" = 6, "Avg Wind Speed" = 7),
                         selected = 4)
```


### Choosing the City/Cities

A Grouped Check button having 3 buttons corresponding to each of the city should be checked for the plot to be visible.

If no cities are chosen, the plot will not be visible.

The default choice is Bangalore.


```{r echo = FALSE}
            checkboxGroupInput(inputId = "city", label = "Choose Cities",
                         choices = list("Bangalore" = 1, "Mumbai" = 2, "Chennai" = 3),
                         selected = 1)
```


### The Plot

The Plot is highly interactive. It is a scatter plot with both lines and points.

Each City is differentiated by colour and the legends are present on the right side of the plot.

Changing any selection on the input side will result in the corresponding change in plot, updated almost instantaneously on a fast machine with good internet speed.

```{r echo = FALSE}
df <- read.csv("May_Weather.csv")
dfB <- subset(df, df$City == "Bangalore")
dfM <- subset(df, df$City == "Mumbai")
dfC <- subset(df, df$City == "Chennai")
df <- cbind(dfB, dfM, dfC)

y_label <- c('','','Max Temperature in Fahrenheit', 'Avg Temperature in Fahrenheit',
             'Min Temperature in Fahrenheit', 'Avg Humidity in %', 'Avg Wind Speed in mph')


renderPlotly({
  
            data <- subset(df, Date >= input$date[1] & Date <= input$date[2])
            y_param <- as.numeric(input$ylabel)
            city <- input$city

            fig <- plot_ly(data, x = ~data$Date)
            fig <- fig %>% layout(
                xaxis = list(title = "Date"),
                yaxis = list(title = y_label[y_param]))
            
            if("1" %in% city){          
                fig <- fig %>% add_trace(y = ~data[[y_param]]
                           , name = 'Bangalore', 
                    type = 'scatter', mode = 'lines+markers',
                    marker = list(size = data[[6]]/7), hoverinfo = 'text',
                    
                    text = ~paste(data[[1]],'on May', data[[2]], 
                    '<br>Max Temp :', data[[3]],'F','<br>Min Temp :', data[[5]],
                    'F','<br>Avg Temp :', data[[4]],'F', '<br>Humidity :',
                    data[[6]],'%','<br>Wind Spd :', data[[7]],'mph')
                    )
            }

            
# Preparing for Mumbai

            if("2" %in% city){ 
            fig <- fig %>% add_trace(y = ~data[[y_param  + 7]], name = 'Mumbai', 
                           mode = 'lines+markers',
                           marker = list(size = data[[6 + 7]]/7), hoverinfo = 'text',
            
                           text = ~paste(data[[1 + 7]],'on May', data[[2 + 7]], 
            '<br>Max Temp :', data[[3 + 7]],'F','<br>Min Temp :', data[[5 + 7]],
            'F','<br>Avg Temp :', data[[4 + 7]],'F', '<br>Humidity :',
            data[[6 + 7]],'%','<br>Wind Spd :', data[[7 + 7]],'mph')
            )
            }
            
# Preparing for Chennai
            
            if("3" %in% city){ 
            fig <- fig %>% add_trace(y = ~data[[y_param  + 14]], name = 'Chennai', 
                            mode = 'lines+markers',
                            marker = list(size = data[[6 + 14]]/7), hoverinfo = 'text',
                                     
                            text = ~paste(data[[1 + 14]],'on May', data[[2 + 14]], 
            '<br>Max Temp :', data[[3 + 14]],'F','<br>Min Temp :', data[[5 + 14]],
            'F','<br>Avg Temp :', data[[4 + 14]],'F', '<br>Humidity :',
            data[[6 + 14]],'%','<br>Wind Spd :', data[[7 + 14]],'mph')
            )
            }
            if(!is.null(city))
            fig
            
                        })
```
